---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
## 
```{r Load Library, message=FALSE, warning=FALSE, include=FALSE}
library(readr)
library(dplyr)
library(ggplot2)
```

## Loading and preprocessing the data

```{r, message=FALSE, warning=FALSE}
activity <- read_csv("~/R Workspace/RepData_PeerAssessment1/activity.csv")
```
```{r}
dim(activity) 
head(activity)
str(activity)
```

## What is mean total number of steps taken per day? ##

### 1 - Calculate the total number of steps taken per day
```{r}
y <- group_by(activity, date)
tot_steps <- summarise(y, sum(steps)) # Sum calculation
head(tot_steps)
```
### 2 - Make a histogram of the total number of steps taken each day

```{r}
plot(tot_steps$date,tot_steps$`sum(steps)`, type = 'h', lwd = 8, xlab = "data", 
     ylab = "Steps for day", col = "gray", main ="The total number of steps taken each day")
```

## 3 - Calculate and report the mean and median of the total number of steps taken per day

**a) - An histogram of the mean number of steps taken each day**

```{r}
z <- group_by(activity, date)
mean_steps <- summarise(z, mean(steps)) # Mean calculation
head(mean_steps)
```

```{r}
plot(mean_steps$date,mean_steps$`mean(steps)`, type = 'h', lwd = 8, xlab = "data", ylab = "Mean steps for day", col = "blue", main ="Steps taken (in mean) each day")
```
#
**b) - An histogram of the median number of steps taken each day**

```{r}
w <- group_by(activity, date)
median_steps <- summarise(w, median(steps)) #Median calculation
head(median_steps)
```
##
```{r}
plot(median_steps$date,median_steps$`median(steps)`, type = 'h', lwd = 8, xlab = "data", ylab = "Median steps for day", col = "orange", main ="Steps taken (in median) each day")
```

## What is the average daily activity pattern? 

```{r}
plot(activity$date,activity$steps, type = 'l',lwd = 1, xlab = "data", 
     ylab = "Steps for day", main ="The total number of steps taken each day")
abline(h = 10766.19, col = "red")
```

## Imputing missing values
```{r}
num_NA <- activity[is.na(activity$steps),] # Count missin value
dim(num_NA)
```

```{r}
t <- activity[activity$steps > 0, ] # Remove zero value
```

```{r}
x <- activity[!is.na(activity$steps),] # Remove missin value
dim(x)
```
##
## Are there differences in activity patterns between weekdays and weekends? 
##