---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

```{r, message=FALSE, warning=FALSE}
library(readr)
library(dplyr)

```

## Loading and preprocessing the data

```{r, message=FALSE, warning=FALSE}
activity <- read_csv("~/R Workspace/RepData_PeerAssessment1/activity.csv")
dim(activity) 
head(activity)
```

## What is mean total number of steps taken per day?

### 1 -Calculate the total number of steps taken per day
```{r}
y <- group_by(activity, date)
tot_steps <- summarise(y, sum(steps))
head(tot_steps)
```
### An histogram of the total number of steps taken each day

```{r}
plot(tot_steps$date,tot_steps$`sum(steps)`, type = 'h', lwd = 8, xlab = "data", ylab = "Total steps for day", col = "gray", main ="The total number of steps taken each day")
```

## Calculate and report the mean and median of the total number of steps taken per day

```{r}
z <- group_by(activity, date)
mean_steps <- summarise(z, mean(steps))
median_steps <- summarise(z, median(steps))
head(mean_steps)
head(median_steps)
```

## Calculate the total number of steps taken per day
```{r}
w <- group_by(activity, date)
median_steps <- summarise(w, median(steps))
head(median_steps)
```

## What is the average daily activity pattern?



## Imputing missing values


```{r}
x <- activity[!is.na(activity$steps),]
dim(x)
```


## Are there differences in activity patterns between weekdays and weekends?
