---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

```{r, message=FALSE, warning=FALSE}
library(readr)
library(dplyr)

```
#####################################
## Loading and preprocessing the data
#####################################
```{r, message=FALSE, warning=FALSE}
activity <- read_csv("~/R Workspace/RepData_PeerAssessment1/activity.csv")
dim(activity) 
head(activity)
```
#######################################################
## What is mean total number of steps taken per day? ##
#######################################################

### 1 - Calculate the total number of steps taken per day
```{r}
y <- group_by(activity, date)
tot_steps <- summarise(y, sum(steps))
head(tot_steps)
```
### 2 - Make a histogram of the total number of steps taken each day

```{r}
plot(tot_steps$date,tot_steps$`sum(steps)`, type = 'h', lwd = 8, xlab = "data", ylab = "Steps for day", col = "gray", main ="The total number of steps taken each day")
```

### 3 - Calculate and report the mean and median of the total number of steps taken per day


### An histogram of the mean number of steps taken each day

```{r}
z <- group_by(activity, date)
mean_steps <- summarise(z, mean(steps))
head(mean_steps)
```

##

```{r}
plot(mean_steps$date,mean_steps$`mean(steps)`, type = 'h', lwd = 8, xlab = "data", ylab = "Mean steps for day", col = "blue", main ="Steps taken (in mean) each day")
```


### An histogram of the median number of steps taken each day
```{r}
w <- group_by(activity, date)
median_steps <- summarise(w, median(steps))
head(median_steps)
```
##

```{r}
plot(median_steps$date,median_steps$`median(steps)`, type = 'h', lwd = 8, xlab = "data", ylab = "Median steps for day", col = "green", main ="Steps taken (in median) each day")
```
#################################################
## What is the average daily activity pattern? ##
#################################################


## Imputing missing values


```{r}
x <- activity[!is.na(activity$steps),]
dim(x)
```

###############################################################################
## Are there differences in activity patterns between weekdays and weekends? ##
###############################################################################